---
title: "Programming Background"
author: "Chengxi Zou"
date: '2022-06-09'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
```

## My thoughts on R

**R vs SAS**

I've taken ST555 3 times which is about SAS programming, it was a hard course and I was struggling with it. One big difference between R and SAS is that in R we could download many useful packages while SAS seems to be already totally constructed so you couldn't do more things on its functionalities, you just use it.

**What functionality do you like about R? What parts do you miss about your other language? Do you consider R a difficult language to learn?**

It's just a few weeks that I've been learning R, I haven't seen much difference between R and SAS in their functionality so far, and I think the logics and the syntax are not that different, so I would not consider R as a totally different language. The plots generated by SAS is more beautiful than that in R in my opinion though. I like the function _install.packages_ in R and I will keep digging into it.

## example R Markdown output. 

create an R code chunk that outputs a plot.

```{r plotexample, echo=TRUE}
plot(iris)
```

run render function in the console:

render("_Rmd/2022-06-09-TheProgrammingBackgroundPostForST558.rmd",output_format = "github_document", output_dir = "_posts/",output_options = list(html_preview = FALSE))