---
title: "Programming Background"
author: "Chengxi Zou"
date: '2022-06-09'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
```

## My thoughts on R

1. R vs SAS

I've taken ST555 3 times which is about SAS programming, it was a hard course and I was struggling with it. One big difference between R and SAS is that in R we could download many useful packages while SAS seems to be already totally constructed so you couldn't do more things on its functionalities, you just use it.

2. What functionality do you like about R? What parts do you miss about your other language? Do you consider R a difficult language to learn?

It's just a few weeks that I've been learning R, I haven't seen much difference between R and SAS in their functionality so far, the logics and the syntax are similar, so I would jsut say I like the function _install.packages_ in R and I will keep digging into it.


## example R Markdown output. 

create an R code chunk that outputs a plot.

```{r plotexample, echo=TRUE}
plot(iris)
```

render("_Rmd/2022-06-09-TheProgrammingBackgroundPostForST558.rmd",output_format = "github_document", output_dir = "_posts/",output_options = list(html_preview = FALSE))