---
title: "This is my 5th Blog!"
author: "Chengxi Zou"
date: '2022-07-24'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE)
```

# My thoughts on R

## **what your current thoughts are in terms of using R for data science - do you think you'll continue to use R going forward?  Why or why not?**

I think R is a great software to do analysis and output some results. However it's not that convenient to download and call a lot of packages every time we do a new analysis. A easy way is to call as many packages as we know before writing the code, but that sounds stupid; otherwise we need to remember the packages and their functions.

In spite of that, I do like R and I think it's suitable for me, more than SAS did.

## **what things are you going to do differently in practice now that you've had this course?**

I'll use R to do analysis and present my results. After having the course I'm pretty good at sitting for hours trying to make my code run, and I've gained a lot of relevant R knowledge.

## **what areas of statistics/data science are you thinking about exploring further?**

I'm interested in predictions, the methods like random forest I learned from the course is really interesting. I was thinking that sometimes statisticians care too much about "statistical significance", what if we really are trying to predict something rather than figure out what's important or not? Then these prediction methods answered my question.

```{r}
library(rmarkdown)

# run render function in the console:

#render("_Rmd/2022-07-24-Third Blog Post.rmd",output_format = "github_document", output_dir = "_posts/",output_options = list(html_preview = FALSE))
```
