---
title: "This is my 3rd Blog!"
author: "Chengxi Zou"
date: '2022-06-09'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
```

## My thoughts on R

**Write a post about what you consider the coolest thing you've learned about programming in R.  Include an example of it (or at least the code to do it) in your post (for instance, if it was ggplot you could read in a data set and create a cool plot).**

I really like ggplot2 package. The base packages in R produces some graphs that are't very fancy, but using the ggplot2 package we can generate some beautiful graphs and it's easy to understand its syntax of "layers".


```{r plotexample, echo=TRUE, message=FALSE, warning=FALSE}
library(rmarkdown)
library(ggplot2)
iris
ggplot(iris, aes(x = Sepal.Length, Petal.Length)) +
geom_boxplot(aes(color = Species)) +
ggtitle("Box Plot Example")
```

```{r plotexample2, echo=TRUE, message=FALSE, warning=FALSE}
ggplot(iris, aes(x = Sepal.Length)) +
geom_histogram(aes(fill = Species), position = "dodge") +
ggtitle("Histogram Example")
```

```{r plotexample3, echo=TRUE, message=FALSE, warning=FALSE}
ggplot(iris, aes(x = Sepal.Length, Petal.Length)) +
geom_point(aes(color = Species)) +
ggtitle("Scatter Plot Example")
```

run render function in the console:

render("_Rmd/2022-06-29-Third Blog Post.rmd",output_format = "github_document", output_dir = "_posts/",output_options = list(html_preview = FALSE))